---
title: "Overview of Gameday"
author: "Beryl Zhuang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview of Gameday}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

Gameday package would allow users to query live.nhle.com to check if your NHLteam
    is listed on the team play on a given day. Also can query live.nhle.com to get the
    scores for a given day.
    
## How to install

The package can be installed directly from github


`install_github("berylzhuang/gameday")`


## Functions included

`gday()` This function returns TRUE if your NHL team plays on a given day and FALSE otherwise.

`scores()` This function takes a date input and returns a data.frame with information about the scores of all games on the given date.


## Examples

`gday()` contains validity checks

* internet connection

* check valid team names/city

* check valid date format (YYYY-MM-DD)

```{r}
library(gameday)
#use default values
gday()

# use both arguments
gday("canucks", "2014-11-21")

```

see `?gday` for detail information on parameters and defaul values.

`scores()` contains validity checks

* internet connection

* check valid date format (YYYY-MM-DD)

```{r}

#use default value
scores()

# input date
scores("2014-11-21")

```

see `?scores` for detail information on parameters and defaul values.


## helper functions
The package contains three helper functions:

`internet_connection()` : check if internet connection is available, returns TRUE or FALSE
`check_date`: check if the date format is YYYY-MM-DD, returns TRUE or FALSE
`check_team_name`: check if the input string is a team name or city name of the NHL teams, returns TRUE or FALSE


## Credits
Thank you Jenny, Bernard and other people who made the tutorial and instructions.
The functions `internet_connection`, `scores()`, and dataset used in the `check_team_name()` are taken from the [homework10](http://stat545-ubc.github.io/hw10_package.html) with modifications.

## Relection
Making this package has been a fun project for me and with a few chanlenges. The key is to `test()`, build and reload, and `document()` frequently and commit working versions before any major changes. This really helps debugging.

* Helper functions and validity check.
The helper functions are mainly writen for validity checks for the two exported functions.
This takes about 50% of the time (write test, debug, add more tests, debug...)

	* key functions of `testthat`:
			- expect_false()
			- expect_true()
			- expect_equal()
			- expect_error()
A good reference on [Testing](http://r-pkgs.had.co.nz/tests.html)

* Add validity checks to the main functions:

`if(TRUE)
stop("show error message here")`

* Save datasets and load them

	- `devtools::use_data()` save a *.rda file in a new folder `\data`
	- `use_data(..., internal = TRUE)` save a `sysdata.rda` at the root folder
	- document the dataset
			- creat a Rscript then `document()`
```{r}
#' A dataset containing arean, NHL team names and lat and long of
#' arean location
#'
#' @format A data frame with 30 rows and 4 variables:
#' \describe{
#'   \item{Areana}{arena name}
#'   \item{team}{team name and its city}
#'   \item{lat}{latitude of the arean location}
#'   \item{long}{longitude of the arean location}
#'   ...
#' }
#' @source \url{http://stat545-ubc.github.io/r_package_data/arena_team.tsv}
"arena.team"
```

			- load the dataset in the functions by `data(arena.team)`
